The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-03-24 doc/paper/skysubtraction.tex
overdue for checkin

>>>>

The first very critical step is to robustly determine the fiber positions in CCD pixel coordinates.
This is performed by identifying peaks in a cross-sectional cut of across the center row (actually a median
cross-section of the central 9 rows).  The correct identification of the 320
fibers per frame can be uniquely determined by demanding a wider spacing between the bundles (about 10 pixels)
relative to the nominal inter-fiber spacing (6.1 pixels on average).  Once the starting peaks and 
identification have been determined, we trace the fiber centers by performing flux-weighted centroids on subsequent rows
using the previous row's center as the intial guess.  This has proven to work spectacularly well on SDSS
flat-fields, and we have yet to uncover a failure mode in over 10000 flat-field frames.
The flux-weighted centroids do have scatter from shot noise, so we fit a 7th order polynomial to each set of
fiber centroids, and the best-fit coefficients are stored to represent the fiber positions on each
flat-field frame.
